Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2014-02-02 structured.tex
2013.10.29 (Alex) Structured section underwent several reworks/rephrasings. Text reviewed. Minor changes to unstructured section.

This section presents a description and analysis of algorithms proposed
to address the topology mismatch problem in structured \p\ networks. The
categorization of the approaches we present here is based on how different
levels of proximity information is gathered and the way peer routing tables are
maintained and used in an effort make overlay hops as efficient as possible. The
categorization is based on previous work found in the
literature~\cite{CDHR2002,CDCR2002,RSS2002}.

%% VM Rephrased as above to keep it analogous to the opening paragraph of
%% the unstructured part.
%%
% This section presents a description and analysis of algorithms proposed
% to address the topology mismatch problem in structured \p\ networks.
% In structured \p\ networks, the construction of the routing tables
% held by participating nodes determines the efficiency of message forwarding.
% Routing tables that closely match the underlying IP topology
% achieve increased performance. As a result, the proposed solutions for
% the topology mismatch problem for structured \p\ networks
% use different levels of proximity
% information to optimize the routing tables used by peers.
% The categorization of the algorithms we present here is based on the
% categorization suggested by previous
% work~\cite{CDHR2002,CDCR2002,RSS2002}.

@@

\emph{Global Soft-State} \cite{XTZ2003} builds a global map to help
choose shorter routing paths, combining the landmark binning method and small
scale distance probes to reveal the proximity properties of the underlying
network. %Figure \ref{fig:global_softstate} presents the landmark
%space and the mapping of the position of the nodes.
This global view of the
state, is made available to all nodes to help them find the best way to
route their messages. \emph{Global Soft-State} operates in two phases:
generation and use of the proximity information. For generating the proximity
information, a hybrid approach is proposed, which uses landmark clustering as a
preprocessing step to select a number of potential nearest neighbor
candidates and then refine the selection by incorporating a
round-trip-time-based scheme to ultimately choose the closest node. For using
the proximity information, the algorithm follows a different path from that of the
classic gossiping approaches for the construction and maintenance of the
overlay. It is based on landmark clustering for generation and strategic
placement of proximity information on the overlay. This information is called a
``map'' and concerns a region of the overlay (part of the Cartesian space in
structures like eCAN\cite{xu_ecan_2002} or a set of nodes sharing a particular
prefix in overlays such as Pastry\cite{antony_pastry_2001}). Thus, each node not
only can access such information from these landmarks but can also subscribe to
relevant \emph{soft states} and get notified on dynamic network changes. A
node may appear in a maximum of $log\left( N \right)$ such
maps.
%%
Although this approach greatly reduces the routing latency to far nodes, it
comes expensive. It is possible to end up with a very large number of regions
each of which has to maintain a map. The fact that a peer may appear in multiple
such maps we can conclude that additional traffic for probing and notifications
renders the approach not scalable \cite{RGJZ2004}. Moreover, to refine measurements
additional inner-bin measurement s are required\cite{WZS2004}. Also improvement
is done within a region because of little knowledge about neighboring zones.

%% VM Removed most of the paragraph below which contains info that we cannot back
%% Rescanned papers and wrote the paragraph below.
%% DO NOT PERMANENTLY DELETE!
%%
% Unfortunately, maintained of several host states at different layers,
% renders any content migration a costly process. Additionally, the method does
% not make any continuing effort to remap
% the overlay structure after nodes successfully join resulting into poor
% adaptation to changing conditions. Although this approach greatly reduces the
% routing latency to far nodes, it is unable to dynamically identify nodes that
% are close to routers and gateways in order to construct the secondary overlay.
% Nevertheless, static recognition of such nodes is currently done based on BGP
% reports and pre-chosen landmarks, sacrificing the self-organizing attribute of
% traditional DHTs.

%
% TODO: SOME DISCUSSION
%
% Xu \textit{et al.} \cite{XTZ2003} state that there are three ways
% generating proximity information
%\begin{itemize}
% \item Expanding Ring Search\\
%Expanding ring search can be of two forms. First it can utilize the multi-cast
%infrastructure in the underlying network in order to emit its messages.
%Unfortunately such infrastructures are not widely deployed thus the
%implementations of this way of generating proximity information is limited to
%blindly flooding the neighborhood to obtain reasonable results.
%
% \item Heuristics\\
%Heuristics are used in order to reduce the blindness of the expanding ring
%search and make realizations more efficient and effective. Unfortunately a
%common problem of all heuristic approaches is the local minimum pitfall in
%which
%the search might be caught into.
%
% \item Landmark Binning\\
%Landmark clustering is based on the view that nodes with similar distances to a
%set of predefined well-known landmark nodes are pretty likely of being close to
%each other. But this approach has its weaknesses as well, such as the fact that
%is a rather coarse grained approximation, therefore not particularly well
%suited
%for differentiating nodes within close distance to each other.
%
%\end{itemize}
%
%

%
% TODO: IN PAPER INTRODUCTION A DISCUSSION ABOUT
%TOPOLOGY-AWARE CAN
%
%Techniques to exploit topology information in overlay
%routing include geographic layout, proximity routing and
%proximity neighbor selection [3]. With geographic layout
%such as topology-aware CAN [12], the overlay structure is
%constrained by underlying network topology. This tech-
%nique, unfortunately, can create uneven distribution of
%nodes in the overlay, increasing the chances of overloading
%nodes and rendering the maintenance cost formidable. Our
%study shows that, for a typical 10,000-node topology-aware
%CAN, 5% nodes occupy 85-98% of the entire Cartesian
%space, and some nodes have to maintain 450-1500 neigh-
%bors. In Proximity routing, physical topology is not consid-
%ered when constructing the overlay.
%

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Unable to identify nodes that are close to routers but it can reduce routing
% latency to far away node by approximately 50-75%.
medium &
% maintenance of node states, subscriptions and notifications need global
% overview of the overlay resulting in high control overhead
high &
% Statically implemented sacrificing the decentralized nature of DHTs and
% thus poorly scaling. Also we can end up with a very large number of regions.
% Because of the fact that a peer may appear in multiple
% such maps we can conclude that additional traffic for probing and notifications
% renders the approach does not scalable.
low
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Mithos}
\emph{Mithos} \cite{WR2003} is a \p\ protocol which incorporates directed
incremental probing to find near optimal node placement, and is an integration
of geographic layout and proximity routing overlay optimization methods.

The bootstrap phase of \emph{Mithos} starts with a subset of existing members as
the first set of candidates, and while the closest nodes are detected by iteratively
probing the neighborhood, the candidate neighbor list is updated. To
avoid local minima, \emph{Mithos} probes all the neighbors within a two-hop distance
from the current minimum before concluding the process.

After finding its first neighbor, the new-coming peer is assigned an ID using
information gathered during the iterative neighbor selection phase. Based on the
two closest nodes found, along with these nodes neighbors and the corresponding
distances a system of virtual springs is set so that the tension of each spring
is inversely proportional to the distance. The system is then left to settle,
and the state in which it settles is used for its ID. The benefit of these
synthetic coordinates are that
they are explicitly used as the node's ID, and distance computations among nodes
can be done in ID space without requiring physical measurements.

The last step of the algorithm is the interconnection among neighbors. \emph{Mithos}
uses a \emph{quadrant-based} mechanism in which each node establishes
a link to the closest neighbor in each quadrant. During forwarding, the next
hop is performed towards a neighbor in the same quadrant as the final
destination. The new coming node may not know of other neighbors in all
quadrants, therefore, the node first identifies neighbors in all quadrants
using a mechanism based on ideas similar to a perimeter walk\footnote{Used in
the Greedy Perimeter Stateless Routing (GPSR) protocol.} and then improves the
results using parallel path processing by taking into account further geometric
properties of node relationships.

One major limitation of \emph{Mithos} is that the protocol cannot effectively
handle dynamic arrivals and departures from the network. In \cite{CCRK2004} it
is claimed to need extensive probing to determine distances and at the same time
its results are evaluated as less accurate than, for example,
GNP \cite{ng_gnp_2001}. Maybe this has also to do with its iterative neighbor
selection process which is reported to be prone to prematurely terminate at
local minima \cite{WSS2005}. Another point that has negative effect to the
scalability of the algorithm is that parts of its spring relaxation technique
require a centralized implementation~\cite{cox_vivaldi_2004}.

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It has very good results in reducing communication latency among peers but its
% efficiency is being constrained by the fact that the proximity is calculated
% at bootstrap, assigning virtual coordinates that are used throughout of a
% nodes life cycle and thus the overlay is not adapting to a high-churn
% environment.
medium &
% Incremental probing is applied in quadrants and in two-hop distance at each
% step that does not generate a lot o control overhead.
medium &
% It is constrained by the fact that the protocol does not respond to dynamic
% peer arrivals and departures
low
\end{tabular}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{LAPTOP}
\emph{LAPTOP} \cite{WLH2007}, organizes the overlay into a tree-based hierarchy
with the goals of reducing hops during message routing as well as minimizing
maintenance overhead. Additionally, a caching scheme is also incorporated so as
to further reduce routing table update costs. It is theoretically shown
that in \emph{LAPTOP}, routing path length is bounded by $O(log_d N)$ and node
joining and leaving in the overlay network is bounded by
$O\left( d log_d N \right)$ hops in a balanced overlay tree, where $N$ is the
number of nodes, and $d$ is the maximum degree of each node. \emph{LAPTOP}
implements the geographical layout approach  and constructs its layout in a
self-organizing and efficient fashion. The physical distances are estimated
with round trip times to a few existing nodes in the overlay network.

Each node is assigned a dot-formated address (e.g 1.3.4). Each octet ranges from
$1$ to $d$, where $d$ is the maximum degree of the nodes. The assignment process
is done by appending a unique octet to the address of each node's parent, while
the root node is assigned address $1$.

@@

The routing scheme is similar to the longest-prefix IP matching scheme. At each
forwarding hop, any message travels up the tree until the first common ancestor
of both source and destination nodes is reached and then starts descending to
arrive to its target. During tree traversals, special entries in the routing
tables, called \emph{routing cache}, are maintained to increase routing
efficiency and achieve finer load balance. Caching enables a node to forward a
message to a better longest-prefix match than that of its direct ancestor making
a larger, quicker and more cost effective step through the overlay and toward
the destination. To improve scalability, the number of child nodes and the
size of the routing cache are limited. In terms of overlay maintenance, \emph{LAPTOP}
incorporates a simple \emph{heartbeat}-based technique where each parent node is
responsible for monitoring its children.

%
%The new comer $N$ locates the root node and the later responds with a list of
%  $L_1$ nodes. $N$ then probes each of the $L_1$ nodes in search for the
% closest one. If the measured RTT to the closest $L_1$ falls into the first
% interval then the new comer becomes a $L_1$ node as well. Otherwise node $N$
% sets the closest $L_1$ node as its potential parent node. This potential
% parent becomes the actual parent if it does not have any other children. If it
% has, $N$ gets a list of these $L_i$ nodes and by measuring the RTT to each of
% them tries to spot a new potential parent in order to repeat the above
% process.
%

% At join process the new coming node is assigned its level label as well as its
% address by its parent node. Additionally, it initializes its routing table
%(with normal and caching entries) as it traverses the overlay in search for
%its parent node.  During a graceful departure, the referred node checks for
%children in the overlay. If it does not have any, it simply notifies its
%parent and leaves. If it has, it selects the child node with the lowest
%round-trip time to it in order to take its place so that the locality
%property is preserved. On the other hand, in the case of an arbitrary
%failure, after the children of the failed node detect their parent's absence
%(through the aforementioned heartbeat mechanism), they start emitting special
%messages to their grandparent node (the address of which is stored during
%join process}. In case of no response from the grandparent node, the children
%invoke the joining process to detect their new parent node.The parent of the
%failed node, aggregates the notifications from the above children nodes for a
%period of time, and then chooses the one with the lowest level label as the
%takeover node. Potential ties are broken by favoring the lower RTT. The
%parent of the failed node, finally informs accordingly all the children about
%the change in the hierarchy.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO: HERE STRUCTURED LANDMARK BINNING APPROACH LIES
%
%Assuming a structured approach based on CAN\cite{ratnasamy_can_2001} and $m$
% landmark nodes. The coordinate space is then partitioned into $m!$ equally
%sized portions, each corresponding to a single ordering of the landmarks. To do
%this, the first dimension is divided into $m$ areas each of which is further
%divided (second dimension) into $m - 1$ sections and so on. Having set this $m$
%dimensional space, at joining time, a node measures the delay to the set of
%landmarks in order to determine its associated bin and thus position itself in
%that portion of the coordinate space associated with its landmark ordering.
%Even though this scheme can
%

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It minimizes routing length, but may suffer load imbalance since nodes higher
% in the tree hierarchy are more likely to route most of the messages in the
% overlay.
medium &
% Heartbeat approach incurs extra control overhead to the network. Fortunately
% involves only the parent and the children of the departing/failing node.
% nodes.
low &
% Seems to scale nicely from 10K- to 1M-node testbeds.
high
\end{tabular}
\end{center}

@@

\cite{KLKP2008} introduces proximity
controls over the vanilla Kademlia protocol's random ID assignment to
optimize the underlying network usage.
% The work in this paper
% can also be considered as a more generic study of incorporating proximity into
% iterative lookup algorithms.
The overlay tier improves its routing performance using a cost metric that is
provided by the underlying tier. Such information can be acquired by
\begin{inparaenum}[\itshape i\upshape)]
  \item measuring previous lookups,
  \item exchanging measurements of other peers or jointly calculating them with
  others, or
  \item using a local database to look up information.
\end{inparaenum}

Regarding routing optimization both techniques of \emph{proximity routing
selection (PRS)} and \emph{proximity neighbor selection (PNS)} are studied.
%%
In \emph{PRS}, the goal is to choose the best next hop during routing a message.
% Due to the fact that the routing in Kademlia is iterative, it is the initiator
% of the lookup that chooses each next hop from a set of candidate nodes.
Plain old Kademlia (\emph{POK}) always chooses the closest node with respect to
the XOR metric but with proximity routing, Kademlia should also choose the node
that exhibits the smallest underlay metric cost, balancing a trade-off between
the overlay and underlay progress distances.
%%
In \emph{PNS}, on the other hand, the goal is to keep peers with the least
contact cost in the routing table. As Kademlia continuously learns about new
peers via incoming requests and an iterative lookup process, no special
algorithm for searching more cost-effective peers is necessary and it simply
chooses the best peers seen so far.

Proximity injection in Kademlia improves locality of connections between peers.
Towards the enhancement of traffic locality, it is suggested to use information
from the MaxMind GeoIP database\footnote{http://www.maxmind.com} and use it to
form clusters of nearby peers. An other alternative method could use Vivaldi
coordinates \cite{cox_vivaldi_2004}, however, it is suggested that the
clustering approach performs better. Specifically when combined with both
\emph{PRS} and \emph{PNS} preserves more than $40\%$ of the messages within an
ISP and allows only a small $6\%$ to go through intercontinental backbones.

\begin{center}
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Uses static information to cluster nodes which is not the most efficient
% approach in dynamic systems
% PNS reduces lookup latencies by 66\% compared to POK
medium &
% 
medium &
% MaxMind is commercial and cannot be used by FOSS P2P systems. Trying to
% expose information from P2P client can result in security issues.
medium
\end{tabular}
\end{center}

>>>>

This section offers description and analysis of algorithms proposed
to address the topology mismatch problem in structured \p\ networks. 
The categorization of the approaches is based on how different
levels of proximity information is gathered as well as  
the way peer routing tables are maintained and used in an effort make hops in
overlays as efficient as possible. 
%%AD what does it really mean this below???
The categorization is based on previous work found in the
literature~\cite{CDHR2002,CDCR2002,RSS2002}.

%%COMM Rephrased as above to keep it analogous to the opening paragraph of
%% the unstructured part.
%%
% This section presents a description and analysis of algorithms proposed
% to address the topology mismatch problem in structured \p\ networks.
% In structured \p\ networks, the construction of the routing tables
% held by participating nodes determines the efficiency of message forwarding.
% Routing tables that closely match the underlying IP topology
% achieve increased performance. As a result, the proposed solutions for
% the topology mismatch problem for structured \p\ networks
% use different levels of proximity
% information to optimize the routing tables used by peers.
% The categorization of the algorithms we present here is based on the
% categorization suggested by previous
% work~\cite{CDHR2002,CDCR2002,RSS2002}.

@@

\emph{Global Soft-State} \cite{XTZ2003} builds a global map to help
choose shorter routing paths. This is accomplished by 
combining the landmark binning method with small
scale distance probes to reveal the proximity properties 
of the underlying network. 
%Figure \ref{fig:global_softstate} presents the landmark
%space and the mapping of the position of the nodes.
This global view of the state is made available to 
\emph{all} nodes to help them find the best way to route their messages. 
%%AD when you say "all" above means what?? all in the structured network?? 
%%	how is the structured network organized?  (a line or 2 for this?)
\emph{Global Soft-State} operates in $2$ phases:
\emph{generation} and \emph{use} of the proximity information. 
For \emph{generating} the proximity information, 
a hybrid approach is proposed: it uses landmark clustering as a
preprocessing step to select a number of potential nearest neighbor
candidates and then, refines the selection by incorporating a
round-trip-time-based scheme to ultimately choose the closest node. 
%% 
The algorithm follows a different path from that of the
classic gossiping approaches for the construction and 
maintenance of the overlay when 
it comes to \emph{use} the proximity information.
%%AD isn't the following sentence somewhat of repetition??? (of what 
%%	is stated above?? 
The approach is based on landmark clustering 
for generation and strategic
placement of proximity information on the overlay. 
This information is called a ``map'' and concerns a 
region of the overlay; 
the latter may be part of the Cartesian space in
structures like \emph{eCAN}~\cite{xu_ecan_2002} or 
a set of nodes sharing a particular
prefix in overlays such as \emph{Pastry}\cite{antony_pastry_2001}. 
%%
Thus, each node not only can access such information from 
these landmarks but can also subscribe to
relevant \emph{soft states} and get notified on dynamic network changes. 
A node may appear in a maximum of $log(N)$ such maps.
%%
Although this approach does reduce the routing latency to far nodes, it
can become expensive as it is 
possible to end up with a very large number of regions
each of which has to maintain a map. 
The fact that a peer may appear in multiple
such maps points into additional traffic for probing and notifications
and so renders the approach not scalable \cite{RGJZ2004}. 
Moreover, to refine measurements
additional inner-bin measurements are needed~\cite{WZS2004}.
Also, improvements within a region can be minimal as there exists
limited knowledge about neighboring zones.
%%AD rephrased what is below -2 lines- as above..
% Also improvement
% is done within a region because of little knowledge about neighboring zones.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% COMM Removed most of the paragraph below which 
%%		contains info that we cannot back
%%
%% Rescanned papers and wrote the paragraph below.
%% DO NOT PERMANENTLY DELETE!
%%
% Unfortunately, maintained of several host states at different layers,
% renders any content migration a costly process. Additionally, the method does
% not make any continuing effort to remap
% the overlay structure after nodes successfully join resulting into poor
% adaptation to changing conditions. Although this approach greatly reduces the
% routing latency to far nodes, it is unable to dynamically identify nodes that
% are close to routers and gateways in order to construct the secondary overlay.
% Nevertheless, static recognition of such nodes is currently done based on BGP
% reports and pre-chosen landmarks, sacrificing the self-organizing attribute of
% traditional DHTs.
%
%
% TODO: SOME DISCUSSION
%
% Xu \textit{et al.} \cite{XTZ2003} state that there are three ways
% generating proximity information
%\begin{itemize}
% \item Expanding Ring Search\\
%Expanding ring search can be of two forms. First it can utilize the multi-cast
%infrastructure in the underlying network in order to emit its messages.
%Unfortunately such infrastructures are not widely deployed thus the
%implementations of this way of generating proximity information is limited to
%blindly flooding the neighborhood to obtain reasonable results.
%
% \item Heuristics\\
%Heuristics are used in order to reduce the blindness of the expanding ring
%search and make realizations more efficient and effective. Unfortunately a
%common problem of all heuristic approaches is the local minimum pitfall in
%which
%the search might be caught into.
%
% \item Landmark Binning\\
%Landmark clustering is based on the view that nodes with similar distances to a
%set of predefined well-known landmark nodes are pretty likely of being close to
%each other. But this approach has its weaknesses as well, such as the fact that
%is a rather coarse grained approximation, therefore not particularly well
%suited
%for differentiating nodes within close distance to each other.
%
%\end{itemize}
%
%
%
% TODO: IN PAPER INTRODUCTION A DISCUSSION ABOUT
%TOPOLOGY-AWARE CAN
%
%Techniques to exploit topology information in overlay
%routing include geographic layout, proximity routing and
%proximity neighbor selection [3]. With geographic layout
%such as topology-aware CAN [12], the overlay structure is
%constrained by underlying network topology. This tech-
%nique, unfortunately, can create uneven distribution of
%nodes in the overlay, increasing the chances of overloading
%nodes and rendering the maintenance cost formidable. Our
%study shows that, for a typical 10,000-node topology-aware
%CAN, 5% nodes occupy 85-98% of the entire Cartesian
%space, and some nodes have to maintain 450-1500 neigh-
%bors. In Proximity routing, physical topology is not consid-
%ered when constructing the overlay.
%
In terms of our $3$ criteria, the approach fares as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Unable to identify nodes that are close to routers but it can reduce routing
% latency to far away node by approximately 50-75%.
medium &
% maintenance of node states, subscriptions and notifications need global
% overview of the overlay resulting in high control overhead
high &
% Statically implemented sacrificing the decentralized nature of DHTs and
% thus poorly scaling. Also we can end up with a very large number of regions.
% Because of the fact that a peer may appear in multiple
% such maps we can conclude that additional traffic for probing and notifications
% renders the approach does not scalable.
low
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Mithos}
\emph{Mithos} \cite{WR2003} is a \p\ protocol which incorporates directed
incremental probing to find near optimal node placement and integrates
geographic layout and proximity routing overlay optimization methods.
%%AD in general some mention of the mismatch problem must be made right???
%%		so that a reasonable connection can be established...

The bootstrap phase of \emph{Mithos} starts with a subset 
of existing members as the initial set of candidates and 
while the closest nodes are detected by iterative
probing of the neighborhood, the candidate neighbor--list gets updated. 
To avoid local minima, \emph{Mithos} probes all the neighbors 
within a two-hop distance from the current minimum 
before concluding the process.

After finding its first neighbor, an 
% new-coming   %%AD overall the term new-coming is somewhat odd.. incoming? 
incoming peer is assigned 
an \emph{ID} using information gathered during 
the iterative neighbor selection phase. 
%%AD use SIMPLE sentences that are well structured to say what u want
Based on the two closest nodes found, along with these nodes neighbors and the corresponding
distances a system of virtual springs is set so that the tension of each spring
is inversely proportional to the distance. 
%%AD the above is impossible to read.. "based on,... along with... " NO!!!
%%AD I am not sure what you are talking about here - I mean below... rework
%%	and simplify.. 
The system is then left to settle,
and the state in which it settles is used for its \emph{ID}. 
The benefit of these synthetic coordinates are that
they are explicitly used as the node's \emph{ID}, 
and distance computations among nodes
can be done in \emph{ID} space without requiring physical measurements.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% upto here %%%%%%%%%%%%%%%%

The last step of the algorithm is the 
interconnection among neighbors. 
\emph{Mithos} uses a \emph{quadrant-based} mechanism in which 
each node establishes a link to the closest neighbor in each quadrant. 
%%AD what is the quadrant??? Hugh??? 
During forwarding, the next hop is performed towards a neighbor 
in the same quadrant of the final destination. 
An incoming node may not know of other neighbors in all
quadrants, therefore, the node first identifies neighbors in all quadrants
using a mechanism based on ideas similar to a perimeter walk~\footnote{Used in
the Greedy Perimeter Stateless Routing (\emph{GPSR}) protocol.}  %%AD ref??
and then improves the results using parallel path processing 
by taking into account further geometric properties of node relationships.
%%AD the above 5-6 lines sounds impressive but there is little help 
%%	for the average ignorant reader.. what is perimeter walk in 
%%	general? how quadrants are formed? What is their relationship?

One major limitation of \emph{Mithos} is that the protocol cannot effectively
handle dynamic arrivals and departures from the network. 
\cite{CCRK2004}~points out the extensive probing to determine 
distances and evaluates \emph{Mithos} results as less accurate
than those derived with \emph{GNP}~\cite{ng_gnp_2001}. 
%%AD what is GNP??? How did it "land" here???
%%
The latter has been also attributed by~\cite{WSS2005} to 
the iterative neighbor selection process which that is 
reportedly prone to premature termination at local minima.
%%
\cite{cox_vivaldi_2004} argues that elements of the protocol's
spring relaxation technique require a centralized implementation 
affecting \emph{Mithos} scalability.
%%AD rephrased what is below as above...
% Another point that has negative effect to the
% scalability of the algorithm is that parts of its spring relaxation technique
% require a centralized implementation~\cite{cox_vivaldi_2004}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In regard to the $3$ criteria, \emph{Mithos} stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It has very good results in reducing communication latency among peers but its
% efficiency is being constrained by the fact that the proximity is calculated
% at bootstrap, assigning virtual coordinates that are used throughout of a
% nodes life cycle and thus the overlay is not adapting to a high-churn
% environment.
medium &
% Incremental probing is applied in quadrants and in two-hop distance at each
% step that does not generate a lot o control overhead.
medium &
% It is constrained by the fact that the protocol does not respond to dynamic
% peer arrivals and departures
low
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{LAPTOP}
\emph{LAPTOP} \cite{WLH2007} organizes the overlay 
%%AD what is the nature of the "structure" overlay here???
into a tree-based hierarchy so that 
hops required during message routing be reduced and 
maintenance overhead be minimized.
A caching scheme is also used so as
to further lower routing table update costs. 
It is theoretically shown that 
\emph{LAPTOP} routing path length is bounded by $O(log_d(N))$ and node
joining and leaving in the overlay network is bounded by
$O(d*log_d(N))$ hops in a balanced overlay tree with $N$ representing the
number of nodes and $d$ the maximum degree of each node. 
\emph{LAPTOP} 
%% implements 
adopts the geographical layout approach  
and constructs its layout in a self-organizing and 
efficient fashion. 
The physical distances are estimated
with round trip times to a few existing nodes in the overlay network.
%%
Each node is assigned a dot-formatted address (e.g., 1.3.4). 
Each octet ranges from
$1$ to $d$.
%  where $d$ is the maximum degree of the nodes. 
%%AD this definition was provided just above.. 
The assignment process is done by appending a unique octet 
to the address of the parent of each node, while
the root node is assigned address $1$.

@@

\emph{LAPTOP}'s routing scheme is similar to the 
longest-prefix \emph{IP} matching scheme. 
At each forwarding hop, a message travels up the tree 
until the first common ancestor of both source and destination nodes 
is reached and then, the message starts descending towards its target. 
During tree traversals, special entries in the routing tables, 
called \emph{routing cache}, 
%%AD clarify - routing caches are the special entries OR the routing tables???
are maintained to increase routing efficiency and achieve finer--load balance. 
Caching enables a node to forward a message to a better 
longest-prefix match than that of its direct ancestor yielding
a larger, quicker and more cost--effective step through the overlay towards
the destination. 
To improve scalability, the number of child nodes and the
size of the routing cache are limited. 
To contain maintenance costs, \emph{LAPTOP} employs 
a simple \emph{heartbeat}-based regime in which 
a parent is responsible for the monitor of its own children.
%%AD rephrased what is below as above.. 
% In terms of overlay maintenance, \emph{LAPTOP}
% incorporates a simple \emph{heartbeat}-based technique 
% where each parent node is
% responsible for monitoring its children.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%The new comer $N$ locates the root node and the later responds with a list of
%  $L_1$ nodes. $N$ then probes each of the $L_1$ nodes in search for the
% closest one. If the measured RTT to the closest $L_1$ falls into the first
% interval then the new comer becomes a $L_1$ node as well. Otherwise node $N$
% sets the closest $L_1$ node as its potential parent node. This potential
% parent becomes the actual parent if it does not have any other children. If it
% has, $N$ gets a list of these $L_i$ nodes and by measuring the RTT to each of
% them tries to spot a new potential parent in order to repeat the above
% process.
%
%
% At join process the new coming node is assigned its level label as well as its
% address by its parent node. Additionally, it initializes its routing table
%(with normal and caching entries) as it traverses the overlay in search for
%its parent node.  During a graceful departure, the referred node checks for
%children in the overlay. If it does not have any, it simply notifies its
%parent and leaves. If it has, it selects the child node with the lowest
%round-trip time to it in order to take its place so that the locality
%property is preserved. On the other hand, in the case of an arbitrary
%failure, after the children of the failed node detect their parent's absence
%(through the aforementioned heartbeat mechanism), they start emitting special
%messages to their grandparent node (the address of which is stored during
%join process}. In case of no response from the grandparent node, the children
%invoke the joining process to detect their new parent node.The parent of the
%failed node, aggregates the notifications from the above children nodes for a
%period of time, and then chooses the one with the lowest level label as the
%takeover node. Potential ties are broken by favoring the lower RTT. The
%parent of the failed node, finally informs accordingly all the children about
%the change in the hierarchy.
%%%
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO: HERE STRUCTURED LANDMARK BINNING APPROACH LIES
%
%Assuming a structured approach based on CAN\cite{ratnasamy_can_2001} and $m$
% landmark nodes. The coordinate space is then partitioned into $m!$ equally
%sized portions, each corresponding to a single ordering of the landmarks. To do
%this, the first dimension is divided into $m$ areas each of which is further
%divided (second dimension) into $m - 1$ sections and so on. Having set this $m$
%dimensional space, at joining time, a node measures the delay to the set of
%landmarks in order to determine its associated bin and thus position itself in
%that portion of the coordinate space associated with its landmark ordering.
%Even though this scheme can
%
\emph{LAPTOP}'s behavior for the $3$ criteria stands as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It minimizes routing length, but may suffer load imbalance since nodes higher
% in the tree hierarchy are more likely to route most of the messages in the
% overlay.
medium &
% Heartbeat approach incurs extra control overhead to the network. Fortunately
% involves only the parent and the children of the departing/failing node.
% nodes.
low &
% Seems to scale nicely from 10K- to 1M-node testbeds.
high
\end{tabular}
}
\end{center}

@@

In order to optimize the underlying network use,
\cite{KLKP2008} introduces proximity
controls over the \emph{vanilla Kademlia} 
protocol's random \emph{ID} assignment.
% The work in this paper
% can also be considered as a more generic study of incorporating proximity into
% iterative lookup algorithms.
In its quest to improve routing performance, the overlay uses 
a cost ``yardstick'' (i.e., metric) provided by the underlying network.
% The overlay tier improves its routing performance using a cost--metric that is
% provided by the underlying tier. 
Such cost information can be acquired by
\begin{inparaenum}[\itshape i\upshape)]
  \item measuring previous lookups,
  \item exchanging or jointly-computing measurements with 
	others, or 
  \item using a local database to look--up information.
\end{inparaenum}

\cite{KLKP2008} exploits $2$ routing techniques: 
\emph{proximity routing selection (PRS)} and 
\emph{proximity neighbor selection (PNS)}.
%%
In \emph{PRS}, the goal is to choose the best next hop while routing a message.
\emph{Plain old Kademlia} (\emph{POK}) always selects the closest--node 
with respect to the \emph{XOR} metric.
With \emph{PRS} in place however, \emph{Kademlia} may also choose 
the node that exhibits the smallest underlay metric cost; in this way, 
it balances a trade-off between the logical overlay and 
actual underlying distances.
%%AD rephrased as above.. the "underlay" I am not sure what it is...
%  but with proximity routing, Kademlia should also choose the node
% that exhibits the smallest underlay metric cost, balancing a trade-off between
% the overlay and underlay progress distances.
%%
In \emph{PNS}, on the other hand, the goal is to keep peers 
with the least contact cost in the routing table. 
%%AD WHAT is this "least contact cost"?? Sounds funny! CHECK
As \emph{Kademlia} continually learns about new
peers via incoming requests and an iterative lookup process, 
%%AD what is this iterative lookup process???
no specialized algorithm is required for searching for 
more cost-effective peers 
and the system simply goes for the best peers ``seen'' thus far.

\emph{Kademlia} proximity injection improves 
locality of connections among peers.
To enhance traffic locality, the use of 
{\sl MaxMind GeoIP} database~\footnote{\url{http://www.maxmind.com}} 
is suggested to form clusters of nearby peers.
To this end, Vivaldi coordinates~\cite{cox_vivaldi_2004} could be 
also used as an alternative for morphing locality. 
\cite{KLKP2008} however suggests that the clustering approach 
when combined with \emph{PRS}/\emph{PNS} helps contain 
$40\%$ of messages within an \emph{ISP} and allows only a $6\%$ 
to go through the backbone.
The behavior of the proposal with respect to the stated criteria is deemed as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Uses static information to cluster nodes which is not the most efficient
% approach in dynamic systems
% PNS reduces lookup latencies by 66\% compared to POK
medium &
% 
medium &
% MaxMind is commercial and cannot be used by FOSS P2P systems. Trying to
% expose information from P2P client can result in security issues.
medium
\end{tabular}
}
\end{center}
